DRAFT Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report

### 2022-10-06 child_single_geo.Rmd
try kable material styling

road_sum <- this_roads %>%
  mutate(distance = st_length(.)) %>%  
  st_set_geometry(., NULL) %>% 
  group_by(road_class) %>%
  summarise(t_miles = sum(distance)/5280,
            miles = format(round(as.numeric(sum(distance)/5280), 1), 
                           digits = 1, nsmall=1, big.mark=","),
            .groups = "drop")
df <- select(road_sum, -t_miles)
colnames(df) <- c("Road Class", "Miles")
knitr::kable(df)
```

@@

```{r, eval=has_both}
df <- this_comb %>% st_set_geometry(., NULL) %>% 
  group_by(road_class, SIDE_OF_RO, TYPE) %>%
  summarize(s_miles = sum(distance)/5280,
            miles = format(round(as.numeric(sum(distance)/5280), 1), 
                           digits = 1, nsmall=1, big.mark=","),
            .groups = "drop")
knitr::kable(select(df,-s_miles))
```

@@

The overall score for pedestrian facilities in {{current_geo}} is `r nice_comma(this_comb_total_score)`, `r getScoreInterpretation(this_comb_total_score)`.

>>>>

road_sum <- this_roads %>%
  mutate(distance = st_length(.)) %>%  
  st_set_geometry(., NULL) %>% 
  group_by(road_class) %>%
  summarise(t_miles = sum(distance)/5280,
            miles = format(round(as.numeric(sum(distance)/5280), 1), 
                           digits = 1, nsmall=1, big.mark=","),
            .groups = "drop")
df <- select(road_sum, -t_miles)
colnames(df) <- c("Road Class", "Miles")
knitr::kable(df) %>%
  kable_material(c("striped", "hover"))
```

@@

```{r, eval=has_both}
df <- this_comb %>% st_set_geometry(., NULL) %>% 
  group_by(road_class, SIDE_OF_RO, TYPE) %>%
  summarize(s_miles = sum(distance)/5280,
            miles = format(round(as.numeric(sum(distance)/5280), 1), 
                           digits = 1, nsmall=1, big.mark=","),
            .groups = "drop")
knitr::kable(select(df,-s_miles)) %>%
  kable_material(c("striped", "hover"))
```

@@

**The overall score for pedestrian facilities in {{current_geo}} is `r nice_comma(this_comb_total_score)`, `r getScoreInterpretation(this_comb_total_score)`.**
